---
title: "Assumptions Exercise"
format: html
editor: visual
---

## 

```{r}
library("tidyverse")
library("ISLR2")
data(Auto)
```

```{r}
summary(Auto)
```

#### Categorical Variables: origin and name

```{r}
car_model <- lm(mpg ~ horsepower + displacement + acceleration + cylinders + origin, data=Auto)
summary(car_model)
```

#### The standard error for cylinders is the greatest compared to all other predictors.

```{r}
Auto %>% group_by(cylinders) %>% count()
```

```{r}
view(Auto)

```

```{r}
list_of_cylinders <- Auto["cylinders"]
to_keep <- c(4,6,8)
to_remove <- c(3,5)

Auto$cylinders <- factor(Auto$cylinders, levels = to_keep)

Auto <- Auto %>% filter(!is.na(cylinders))

table(Auto$cylinders)
                  
```

```{r}
plot(car_model)
```

```{r}
plot(car_model, which = 1)
```

```{r}
plot(car_model,which=2)
```

```{r}
ggplot(Auto, aes(x = mpg, y = displacement, col = cylinders)) +
  geom_point() +
  labs(col = "Cylinders")
```

#### I think a transformation is needed because this pattern is non linear breaking the linearity assumption. I will try both and see which transformation is better.

```{r}
ggplot(Auto, aes(x = mpg, y = log(displacement), col = cylinders)) +
  geom_point() +
  labs(col = "Cylinders")
  
ggplot(Auto, aes(x = mpg, y = displacement^2, col = cylinders)) +
  geom_point() +
  labs(col = "Cylinders")


```

```{r}
#I am going to change displacement to log transformation to see if the standard error is better:

displaced_model_log <- lm(mpg~ displacement + log(displacement),data=Auto)

tidy(displaced_model_log, conf.int=TRUE)
plot(displaced_model_log, which = 1)
plot(displaced_model_log, which = 2)

Auto$displacement_squared <- Auto$displacement^2
displaced_model_quad <- lm(mpg~ displacement + displacement_squared,data=Auto)

tidy(displaced_model_quad, conf.int=TRUE)
plot(displaced_model_quad, which = 1)
plot(displaced_model_quad, which = 2)


```

#### From my analysis the standard error decreased significantly when we used a quadratic transformation of the displacement variable.
